Стохастический метод Ньютона \\ с различным семплингом

### 2023-05-03 paper/Stochastic Newton with Arbitrary Sampling.tex
Renamed paper
Updated presentation

		The interpretation is that each of $\tau$ processors chooses on of the train objects $i \in [n]$. If several processors have chosen the same train object, then only one of them gets access to it. This strategy is very easy to implement in terms of parallel computation. Besides, when batches are small, we have $\tau \ll n$ and then $\tau$-independent sampling is a good approximation of $\tau$-nice variant.

@@

	\section{Conclusion}
	So, we do a comparison of different sampling strategies applied to the Stochastic Newton algorithm (\ref{SN}). Firstly, we generalize the convergence rate estimations to all Doubly Uniform strategies and determine the practical equivalence of the most common representatives of this type of sampling (Lemma \ref{lemma:4}, Equation \ref{DU convergence}, Figure \ref{fig:1}). Secondly, we obtain that the Importance Sampling is not likely to outperform the usual $\tau$-nice strategy, and has been noticed to be inferior in practice (Figure \ref{fig:2}). Finally, the improvements come from applying the consecutive strategy (Figure \ref{fig:3}). This effect is encouraging, and therefore needs to be studied more precisely.

>>>>

		The interpretation is that each of $\tau$ processors chooses one of the train objects $i \in [n]$. If several processors have chosen the same train object, then only one of them gets access to it. This strategy is very easy to implement in terms of parallel computation. Besides, when batches are small, we have $\tau \ll n$ and then $\tau$-independent sampling is a good approximation of $\tau$-nice variant.

@@

	\section{Conclusion}
	So, we do a comparison of different sampling strategies applied to the Stochastic Newton algorithm (\ref{SN}). Firstly, we generalize the linear convergence rate estimations to all Doubly Uniform strategies and determine the practical equivalence of the most common representatives of this type of sampling (Lemma \ref{lemma:4}, Equation \ref{DU convergence}, Figure \ref{fig:1}). Secondly, we obtain that the Importance Sampling is not likely to outperform the usual $\tau$-nice strategy, and has been noticed to be inferior in practice (Figure \ref{fig:2}). Finally, the improvements come from applying the consecutive strategy (Figure \ref{fig:3}). This effect is encouraging, and therefore needs to be studied more precisely.

### 2023-05-03 slides/Презентация.tex
Updated presentation

\documentclass{beamer}
\beamertemplatenavigationsymbolsempty
\usecolortheme{beaver}
\setbeamertemplate{blocks}[rounded=true, shadow=true]
\setbeamertemplate{footline}[page number]
%
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{amssymb,amsfonts,amsmath,mathtext,amsthm, mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{subfig}
\usepackage[all]{xy} % xy package for diagrams
\usepackage{array}
\usepackage{multicol}% many columns in slide
\usepackage{hyperref}% urls
\usepackage{hhline}%tables
% Your figures are here:
\graphicspath{ {fig/} {../fig/} }

@@

\begin{columns}[c]
\column{0.5\textwidth}
    \begin{block}{Однородные стратегии}

    	Любое множество размера $j$ выбирается с одинаковой вероятностью, $P(|\hat S| = j) = q_j$

    	\begin{itemize}
    		\item $\tau$-nice семплинг \\
    		$ q_\tau = 1 $
    		\item $\tau$-независимый семплинг \\
    		$ q_k = \binom{n}{k}c_k, k = 1, 2, ..., \tau $
    		\item $(\tau, p_b)$-биномиальный семплинг \\
    		$ q_k = \binom{\tau}{k}p_b^k(1 - p_b)^k, k \leqslant \tau $
    	\end{itemize}
    \end{block}
\column{0.5\textwidth}
	\begin{block}{Независимые стратегии}
		Теперь каждый объект $i$ включается в множество $S$ независимо с вероятностью $p_i$.
	\end{block}
    \begin{block}{Importance sampling}
    	Каждая $f_i$ имеет свою константу Липшица $L_i$
    	$$p_i = \frac{L_i}{\sum \limits_{i=1}^n L_i}$$
    \end{block}
\end{columns}

@@

	\begin{block}{Средний квадрат незвяки}
		$\mathcal W^k \overset{\text{def}} = \frac{1}{n} \sum \limits_{i=1}^n \| w_i^k - x^* \|^2$
	\end{block}

\begin{columns}[c]
\column{0.5\textwidth}
	\begin{block}{Однородные стратегии}
		Пусть $p = \frac{\mathbb E[|\hat S|]}{n}$. Тогда \\
		$ \mathbb E_k[\mathcal W^{k+1}] \leqslant \left( 1 - \frac{3}{4}p \right) \mathcal W^k$ \\
		Результат получается одинаковым для любой стратегии. Поэтому при равных $p$ различие будет только в удобстве реализаций стратегий
	\end{block}
\column{0.5\textwidth}
	\begin{block}{Независимые стратегии}
		Пусть фиксировано матожидание размера батча $\mathbb E_k[|\hat S^k|] = \tau$. Тогда	$ \mathbb E_k[\mathcal W^{k+1}] $ будет минимально, если некоторые $p_i$ равны 1, возможно одно $p_i \in(0,1)$, а остальные равны $0$.
	\end{block}

	\begin{block}{Importance sampling}
		{\color{red} Предстоит доработать}
	\end{block}

>>>>

\documentclass{beamer}
\beamertemplatenavigationsymbolsempty
\usecolortheme{beaver}
\setbeamertemplate{blocks}[rounded=true, shadow=true]
\setbeamertemplate{footline}[page number]
%
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{amssymb,amsfonts,amsmath,mathtext,amsthm,mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{subfig}
\usepackage[all]{xy} % xy package for diagrams
\usepackage{array}
\usepackage{multicol}% many columns in slide
\usepackage{hyperref}% urls
\usepackage{hhline}%tables
% Your figures are here:
\graphicspath{ {fig/} {../fig/} }

@@

\begin{columns}[c]
\column{0.5\textwidth}
    \begin{block}{Однородные стратегии}	
    	Любое множество размера $j$ выбирается с одинаковой вероятностью, $P(|\hat S| = j) = q_j$
    	Пример: $\tau$-nice семплинг \\
    		$$ q_\tau = 1 $$
    \end{block}
	\begin{block}{Независимые стратегии}
		Теперь каждый объект $i$ включается в множество $S$ независимо с вероятностью $p_i$.
	\end{block}
\column{0.5\textwidth}
    \begin{block}{Importance sampling}
    	Каждая $f_i$ имеет свою константу Липшица $H_i$
    	$$p_i = \frac{H_i}{\sum \limits_{i=1}^n H_i}$$
    \end{block}
	\begin{block}{Последовательная стратегия}
		Проходить по данным в порядке, заданном случайное перестановкой
	\end{block}
\end{columns}

@@

\begin{columns}[c]
\column{0.5\textwidth}
	\begin{block}{Средний квадрат незвяки}
		$\mathcal W^k \overset{\text{def}} = \frac{1}{n} \sum \limits_{i=1}^n \| w_i^k - x^* \|^2$
	\end{block}
	\begin{block}{Однородные стратегии}
		Пусть $p = \frac{\mathbb E[|\hat S|]}{n}$. Тогда \\
		$ \mathbb E_k[\mathcal W^{k+1}] \leqslant \left( 1 - \frac{3}{4}p \right) \mathcal W^k$ \\
		Результат получается одинаковым для любой стратегии. Поэтому при равных $p$ различие будет только в удобстве реализаций стратегий
	\end{block}
\column{0.5\textwidth}
	\begin{block}{Независимые стратегии}
		Пусть фиксировано матожидание размера батча $\mathbb E_k[|\hat S^k|] = \tau$. Тогда	$ \mathbb E_k[\mathcal W^{k+1}] $ будет минимально, если некоторые $p_i$ равны 1, возможно одно $p_i \in(0,1)$, а остальные равны $0$. "Аппроксимируется" последовательной стратегией
	\end{block}

	\begin{block}{Importance sampling}
		Теоретических гарантий сходимости нет
	\end{block}
